SAT Competition 2020\tnoteref{title}

### 2021-01-11 paper/main.tex
ranking robustness plot dump

\begin{table}
\caption{Parallel (SAT)}
\label{tab:parallelSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2853.7 & 153 & {\bf pmcompspsthirty} \\
 2 & 2913.6 & 154 & {\bf painlessmaplevone} \\
(2)& 3082.7 & 151 & painlessmaplevtwo \\
(1)& 3196.9 & 148 & pmcompspsixty \\
 3 & 3805.9 & 133 & {\bf plingeling} \\
   & 4048.3 & 130 & manyglucosesixty \\
   & 4076.2 & 130 & manyglucosethirty \\
   & 4675.4 & 119 & syrupscavel \\
   & 4907.1 & 114 & treengeling \\
   & 6337.5 & 85 & abcdsatptwenty \\
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Claud (ALL)}
\label{tab:claud}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2603.8 & 299 & {\bf mallobecs} \\
 2 & 3146.8 & 278 & {\bf toposat} \\
 3 & 4797.6 & 213 & {\bf slime} \\
   & 6800.8 & 132 & paracooba \\
   & 7299.0 & 110 & ctsat \\
   & 8468.3 & 62 & paracoobamarch \\
\end{tabular}
\end{table}

@@

@@

Kochemazov et al. improved three-tier clause-management by persting \todo{Please check "persting"!}
additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}. 
As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.

@@

\multirow{3}{*}{Zhang, Cai}
    & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
 &  & \solbert{Rel. noTimeParam} & \\
 &  & \solbert{Rel. newTech} & \secondo, \firsts\\
\hline

@@

\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{GlucoseSyrup}~\cite{ManySat}.

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSAT}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}.

@@

\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three-way merge of its local export and the two incoming buffers. 
The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{}.

\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{}.

@@

\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Glucose3,Toposat2}. 
\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and MPI \todo{Please spell out MPI once.}
to share clauses between machines~\cite{ManySat,Proceedings}.

\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting.

@@

\solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{SlimeSATRace2019}. 
The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{}. 
Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.

@@

\subsection{Contributions to VBS}

Everything could be done separately for (ALL, SAT, UNSAT)

3X VBS

Greedy cover

Fair split strategy

Z3 strategy

Maxent Nash

Van Gelder ?

>>>>

\begin{table}
\caption{Parallel (SAT)}
\label{tab:parallelSAT}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2853.7 & 153 & {\bf pmcompspsthirty} \\
 2 & 2913.6 & 154 & {\bf painlessmaplevone} \\
(2)& 3082.7 & 151 & painlessmaplevtwo \\
(1)& 3196.9 & 148 & pmcompspsixty \\
 3 & 3805.9 & 133 & {\bf plingeling} \\
   & 4048.3 & 130 & manyglucosesixty \\
   & 4076.2 & 130 & manyglucosethirty \\
   & 4675.4 & 119 & syrupscavel \\
   & 4907.1 & 114 & treengeling \\
   & 6337.5 & \phantom{0}85 & abcdsatptwenty \\
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Claud (ALL)}
\label{tab:claud}
\begin{tabular}{cccl}
place & PAR-2 score & num. solved & solver \\
\hline
 1 & 2603.8 & 299 & {\bf mallobecs} \\
 2 & 3146.8 & 278 & {\bf toposat} \\
 3 & 4797.6 & 213 & {\bf slime} \\
   & 6800.8 & 132 & paracooba \\
   & 7299.0 & 110 & ctsat \\
   & 8468.3 & \phantom{0}62 & paracoobamarch \\
\end{tabular}
\end{table}

@@

\includegraphics[width=0.5\textwidth]{stability/50-50-sat-unsat_random_sampling_scores.png}%
\includegraphics[width=0.5\textwidth]{stability/276_instances_random_sampling_scores.png}
\includegraphics[width=0.5\textwidth]{stability/ALL_random_smpling_correlations.png}%
\includegraphics[width=0.5\textwidth]{stability/SAT_randomSampling_correlations.png}
\includegraphics[width=0.5\textwidth]{stability/UNSAT_randomSampling_correlations.png}

\includegraphics[width=\textwidth]{stability/fam_leave_one_out_corr.png}

@@

Kochemazov et al. improved three-tier clause-management by persisting
additional clauses through hash-based detection of repeatedly learned clauses and presented their award winning~\solver{MapleLCMDistChronoBT-DL} to SAT Race~2019~\cite{Kochemazov:SC2019:MapleChronoBTDL}. 
As can be seen in Table~\ref{tab:solvers-incremental}, numerous submissions to SAT Competition~2020 are forks of some recently award winning \solver{Maple} solver.

@@

\multirow{2}{*}{Zhang, Cai}
    & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
% &  & \solbert{Rel. noTimeParam} & \\
 &  & \solbert{Rel. newTech} & \secondo, \firsts\\
\hline

@@

\solver{ManyGlucose} was submitted in \solver{32 core} and \solver{64 core} variants. 
The \solver{32 core} variant received two awards in this competition: one third place in the Main track and another third place in the Unsat track. 
\solver{ManyGlucose} is a fork of \solver{GlucoseSyrup} that uses strategies known from \solver{ManySat} to achieve deterministic solver behaviour~\cite{Audemard:2018:GlucoseSyrup}~\cite{Audemard:2014:LazyClauseExchange}~\cite{Hamadi:2009:ManySat}.

@@

\solver{Mallob} is a fork of the generic massively parallel SAT solver \solver{HordeSAT}~\cite{Balyo:2015:HordeSATs}. 
\solver{Mallob} performs dynamic load balancing through \emph{malleable job scheduling} in case the input contains several SAT instances of varying priorty. 
This functionality is disabled in the submitted variant \solver{Mallob Mono}.

@@

\solver{Mallob} shares clauses by organizing solvers in a binary tree in which clauses are asynchronously aggregated in a buffer which is passed along this tree from leafs to the root. 
Each node performs a three-way merge of its local export and the two incoming buffers. 
The aggregate that approaches the root of the binary tree is then broadcast to all solvers~\cite{Schreiber:SC2020}.

\solver{Mallob} uses a global clause size limit and a dynamic limit for the sharing buffer, which depends on the position in the binary tree and grows while getting closer to the root. 
Clauses are sorted by their size during aggregation, such that smaller clauses are preferred over longer clauses. 
Duplicates are avoided by using a bloom filter which is periodically cleared~\cite{Schreiber:SC2020}.

@@

\solver{TopoSAT~2} is a massively parallel SAT solver build from \solver{Glucose~3}~\cite{Audemard:2018:Glucose}~\cite{Ehlers:2018:Toposat2}. 
\solver{TopoSAT~2} uses lock-free clause-exchange for solvers running on the same matching, and Message Passing Interface (MPI) to share clauses between machines~\cite{Hamadi:2009:ManySat}. 
\solver{TopoSAT~2} strengthens clauses before export and delays clause import until the trail-size reaches a local minimum. 
\solver{Toposat~2} diversifies via the strategies used for branching, restarting and clause forgetting~\cite{Ehlers:SC2020}.

@@

\solver{Slime} is built from \solver{MapleLCMDistChronoBT} and was first submitted as a sequential solver to SAT Race~2019 with a new phase selection heuristic~\cite{Riveros:SC2019}. 
The new submitted version of \solver{Slime} comes with periodic randomization in geometrically increasing intervals~\cite{Riveros:SC2020}. 
Even thought its sequential version was unsuccessful in the Main track, the MPI-based cloud version of \solver{Slime} won the third price in the Cloud track.

@@

\subsection{Contributions to the Virtual Best Solver}

The Virtual Best Solver (VBS) is a fictitious solver consisting 
of all the solvers that actually participated in the competition (or a specific track)
and an oracle which, when given an input instance,
invokes to run the actual solver which performed the best on that instance.
In this way, the performance of the VBS highlights a certain upper bound 
on performance achievable in principle by the technology 
of the participating solvers (cf. the figures in Section~\ref{sec:results}).

One can see that the VBS solves all the instances that
were solved by at least one solver and solves each instance in the best observed time.
By quantifying how much each participating solver contributes
to the performance of the VBS, we may attempt to establish which
technology (as represented by the solvers) is the most important
(and to what degree) in the observed state of the art of SAT solving.
We came up with the following three related metrics conceptually derived
from the notion of VBS:
\begin{description}
\item[VBS1]
``The fastest takes it all'':
For each solver we count the number of times, it was the fastest to solve an instance.
\item[VBS2]
``Time aware, but proportional'':
A solver $S$ solving an instance $I$ in time $T^S_I$ accrues 
the following fraction of a point for solving $I$:
$T^\mathit{VBS}_I/T^S_I$, where $T^\mathit{VBS}_I$ is the solution time of the best solver on $I$.
\item[VBS3]
``Split the point for solving'':
We award each solver $S$ solving an instance $I$ the fraction $1/|\mathcal{S}_I|$ of points, where
$\mathcal{S}_I$ is the set of solvers solving $I$.
\end{description}
We remark that the sum of VBS1 points, as well as VBS3 points, computed across all the solvers
is equal to the number of instances solved by at least one solver (later denoted \emph{total}).
This is obvious for VBS1, as exactly one solver scores a point for solving an instance.
In the case of VBS3, where we discard the information about the solution times, 
we evenly split the one point reward for solving an instance to those solvers which were successful on it.

In contrast, VBS2 does not have this property as it in general distributes more than one point per instance.
Similarly to VBS1, it takes the solution time into account,
and similarly to VBS3 it does not award just the best solver on an instance.
For example, being twice as slow on an instance than the fastest solver results in a half point awarded.
And, if all the solvers solve an instance with the same solution time,
each solver scores a whole point for that instance.

\begin{table}
\caption{VBS metrics for the results of the Main track, all instances. 
The total number of solved problems was 317. 
There were 60 (non-disqualified) solvers (and their configurations).
Each table shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainALL}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
46 & 11.5 & Kissat-sc2020-unsat \\
37 & \phantom{0}9.2 & Kissat-sc2020-sat \\
22 & \phantom{0}5.5 & Kissat-sc2020-default \\
14 & \phantom{0}3.5 & Maple\_CM+dist+sattime2s+- \\
13 & \phantom{0}3.2 & cryptominisat-ccnr-lsids \\
13 & \phantom{0}3.2 & Maple-LCM-Dist-alluip-trail \\
12 & \phantom{0}3.0 & Relaxed\_LCMDCBDL \\
11 & \phantom{0}2.8 & upGlucose-3.0\_PADC \\
10 & \phantom{0}2.5 & CaDiCaL-sc2020 \\
\phantom{0}9 & \phantom{0}2.2 & Maple\_CMused+dist \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
129.8 & 32.4 & Kissat-sc2020-sat \\
120.1 & 30.0 & Kissat-sc2020-default \\
113.6 & 28.4 & Kissat-sc2020-unsat \\
\phantom{0}91.0 & 22.7 & cryptominisat-ccnr-lsids \\
\phantom{0}87.0 & 21.7 & cryptominisat-ccnr \\
\phantom{0}82.0 & 20.5 & cadical-alluip-trail \\
\phantom{0}81.9 & 20.5 & cadical-alluip \\
\phantom{0}81.8 & 20.5 & CaDiCaL-sc2020 \\
\phantom{0}81.0 & 20.2 & Relaxed\_LCMDCBDL\_newTech \\
\phantom{0}80.5 & 20.1 & Relaxed\_LCMDCBDL \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
11.7 & 2.9 & Kissat-sc2020-default \\
10.8 & 2.7 & Kissat-sc2020-unsat \\
10.4 & 2.6 & Relaxed\_LCMDCBDL\_newTech \\
\phantom{0}9.9 & 2.5 & Kissat-sc2020-sat \\
\phantom{0}9.8 & 2.4 & cadical-alluip \\
\phantom{0}9.8 & 2.4 & cadical-alluip-trail \\
\phantom{0}9.4 & 2.3 & Relaxed\_LCMDCBDL \\
\phantom{0}9.4 & 2.3 & CaDiCaL-sc2020 \\
\phantom{0}8.7 & 2.2 & cadical-trail \\
\phantom{0}8.3 & 2.1 & cryptominisat-walksat \\
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{VBS metrics for the results of the Main track, SAT instances. 
The total number of solved problems was 183. 
There were 60 (non-disqualified) participating solvers.
Each table always shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainSAT}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
27 & 14.8 & Kissat-sc2020-sat \\
14 & \phantom{0}7.7 & Maple\_CM+dist+sattime2s+- \\
12 & \phantom{0}6.6 & Kissat-sc2020-default \\
10 & \phantom{0}5.5 & Relaxed\_LCMDCBDL \\
\phantom{0}8 & \phantom{0}4.4 & CaDiCaL-sc2020 \\
\phantom{0}8 & \phantom{0}4.4 & Kissat-sc2020-unsat \\
\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids-nolimits \\
\phantom{0}7 & \phantom{0}3.8 & cryptominisat-ccnr-lsids \\
\phantom{0}6 & \phantom{0}3.3 & cadical-trail \\
\phantom{0}6 & \phantom{0}3.3 & cryptominisat-ccnr-nolimits \\

\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
68.5 & 37.4 & Kissat-sc2020-sat \\
46.3 & 25.3 & Kissat-sc2020-default \\
44.1 & 24.1 & cryptominisat-ccnr-lsids \\
42.2 & 23.0 & Relaxed\_LCMDCBDL\_newTech \\
41.8 & 22.9 & cryptominisat-ccnr-lsids-nolimits \\
40.9 & 22.3 & cryptominisat-ccnr \\
40.6 & 22.2 & Relaxed\_LCMDCBDL \\
39.4 & 21.5 & cryptominisat-ccnr-nolimits \\
35.2 & 19.2 & cryptominisat-walksat-nolimits \\
32.8 & 17.9 & cryptominisat-walksat \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
8.0 & 4.4 & Relaxed\_LCMDCBDL\_newTech \\
7.0 & 3.8 & Relaxed\_LCMDCBDL \\
6.5 & 3.6 & cryptominisat-walksat-nolimits \\
5.8 & 3.2 & cryptominisat-walksat \\
5.6 & 3.0 & Kissat-sc2020-sat \\
5.4 & 3.0 & cryptominisat-ccnr-lsids \\
5.4 & 3.0 & Kissat-sc2020-default \\
5.4 & 2.9 & cryptominisat-ccnr \\
5.2 & 2.8 & cadical-alluip \\
5.2 & 2.8 & cadical-alluip-trail \\
\end{tabular}
\end{center}
\end{table}

\begin{table}
\caption{VBS metrics for the results of the Main track, UNSAT instances. 
The total number of solved problems was 134. 
There were 60 (non-disqualified) participating solvers.
Each table always shows the first ten solvers sorted according to the respective metric.}
\label{tab:vbsMainUNSAT}
\begin{center}
\begin{tabular}{ccl}
VBS1 & percent total & solver \\
\hline
38 & 28.4 & Kissat-sc2020-unsat \\
11 & \phantom{0}8.2 & Maple-LCM-Dist-alluip-trail \\
10 & \phantom{0}7.5 & Kissat-sc2020-default \\
10 & \phantom{0}7.5 & Kissat-sc2020-sat \\
\phantom{0}8 & \phantom{0}6.0 & Maple\_CMused+dist \\
\phantom{0}6 & \phantom{0}4.5 & cryptominisat-ccnr-lsids \\
\phantom{0}6 & \phantom{0}4.5 & upGlucose-3.0\_PADC \\
\phantom{0}3 & \phantom{0}2.2 & MapleLCMDistChronoBT-f2trc \\
\phantom{0}3 & \phantom{0}2.2 & glucose3.0\_\_proofs \\
\phantom{0}3 & \phantom{0}2.2 & DurianSat \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS2 & percent total & solver \\
\hline
86.3 & 64.4 & Kissat-sc2020-unsat \\
73.8 & 55.1 & Kissat-sc2020-default \\
61.3 & 45.7 & Kissat-sc2020-sat \\
55.4 & 41.3 & MapleLCMDistChronoBT-f2trc-s \\
55.0 & 41.0 & DurianSat \\
53.6 & 40.0 & Maple-LCM-Dist-alluip-trail \\
53.3 & 39.8 & MapleLCMDistChronoBT-f2trc \\
52.4 & 39.1 & MapleLCMDistChronoBT-DL-f2trc \\
51.7 & 38.6 & Maple\_CMused+dist \\
51.6 & 38.5 & ExMapleLCMDistChronoBT\_\_PADC\_DL \\
\end{tabular}
\end{center}
\begin{center}
\begin{tabular}{ccl}
VBS3 & percent total & solver \\
\hline
6.7 & 5.0 & Kissat-sc2020-unsat \\
6.2 & 4.7 & Kissat-sc2020-default \\
4.6 & 3.4 & cadical-trail \\
4.6 & 3.4 & cadical-alluip \\
4.6 & 3.4 & cadical-alluip-trail \\
4.3 & 3.2 & Kissat-sc2020-sat \\
4.2 & 3.1 & CaDiCaL-sc2020 \\
3.4 & 2.5 & MapleLCMDistChronoBT-f2trc-s \\
3.3 & 2.5 & exp\_V\_LGB\_MLD\_CBT\_DL \\
3.0 & 2.3 & MapleLCMDistChronoBT-DL-f2trc \\
\end{tabular}
\end{center}
\end{table}

\todo{Probably hide tab:vbsMainSAT and tab:vbsMainUNSAT.}

Table~\ref{tab:vbsMainALL} renders the just described three metrics applied 
to the full results of the Main track. We can see that the respective leaderboards 
are generally dominated by Kissat-sc2020 and its configurations.
VBS1 tells us that Kissat-sc2020-unsat was most often the fastest solver,
in particular on \SI{11.5}{\percent} of all the solved instances.

VBS2 highlights as first Kissat-sc2020-sat. Its leading \SI{32.4}{\percent} of total is a bit harder to 
interpret: A solver can score \SI{32.4}{\percent} of VBS2 total
by solving \SI{32.4}{\percent} of the solved instances in the best observed time
and no others. But we know, thanks to its VBS1, that Kissat-sc2020-sat solved \SI{9.2}{\percent}
of the solved instances in the best observed time (and some others).
A solver can also score \SI{32.4}{\percent} of VBS2 total by solving all the solved instances,
but always being roughly 3 times slower than the VBS. 
Kissat-sc2020-sat lies obviously somewhere between these two extremes.

Finally, according to VBS3, the best solver is Kissat-sc2020-default with 11.7 points,
which amounts to \SI{2.9}{\percent} of the distributed total score.
The VBS3 metric is generally the most evenly distributed one,
at least among the first 10 solvers.
(The last solver got 0.5 points which is \SI{0.123}{\percent} of total.)
One can conclude from this that most of the benchmarks are solved
by most of the well performing solvers.

\subsection{Greedy set cover}
Another perspective on how much each solver contributes to the state of the art
can be obtained by attempting to construct a sequential schedule of solvers 
(rather then relying on an oracle to pick one for each instance, as with VBS)
and looking at how big role each solvers plays in such a schedule. Since constructing 
an optimal schedule tends to be computationally hard, we start here by 
presenting a useful efficient alternative -- a greedy set cover approach.

With greedy set cover, we start with an empty schedule and iteratively consider 
each solver for the addition to the schedule obtained so far, picking the one
with the highest ``marginal contribution'' in terms of the number of problems
the new schedule will be able to solve. This is perhaps best demonstrated on
the actual data from the competition, again taking the Main track results.

\begin{table}
\caption{A greedy set cover of the solved instances by solvers of the Main track.}
\label{tab:gscMain}
\begin{center}
\begin{tabular}{clccc}
Iteration & selected solver & (num. solved) & contributes & covered so far \\
\hline
\phantom{0}1 & Kissat-sc2020-sat & 264 & 264 & 264 \\
\phantom{0}2 & cadical-alluip & 250 & \phantom{0}22 & 286 \\
\phantom{0}3 & MapleLCMDistChronoBT-f2trc-s & 214 & \phantom{0}10 & 296 \\
\phantom{0}4 & Relaxed\_LCMDCBDL\_newTech & 253 & \phantom{00}6 & 302 \\
\phantom{0}5 & Kissat-sc2020-unsat & 238 & \phantom{00}4 & 306 \\
\phantom{0}6 & cryptominisat-walksat & 243 & \phantom{00}3 & 309 \\
\phantom{0}7 & Relaxed\_LCMDCBDL & 245 & \phantom{00}3 & 312 \\
\phantom{0}8 & cryptominisat-ccnr-lsids & 248 & \phantom{00}1 & 313 \\
\phantom{0}9 & exp\_V\_LGB\_MLD\_CBT\_DL & 194 & \phantom{00}1 & 314 \\
10 & MapleLCMDistChronoBT-DL-f2trc & 220 & \phantom{00}1 & 315 \\
11 & MapleLCMDistChronoBT-DL-v3 & 211 & \phantom{00}1 & 316 \\
12 & cryptominisat-walksat-nolimits & 140 & \phantom{00}1 & 317 \\

\end{tabular}
\end{center}
\end{table}

A greedy set cover of the solved instances by solvers of the Main track is presented 
in Table~\ref{tab:gscMain}. In the first iteration, the solver which solved the highest number 
of instances is selected; in our case it was Kissat-sc2020-sat with 264 instances
as we know already from Table~\ref{tab:mainALL}.
Given those 264 instances as already covered, cadical-alluip was the best in further contributing
to the set by additional 22 instances in iteration 2.
We can see that the further iterations tend to add very little,
with the final 5 iterations adding one instance each. Note that each solver
that managed to solve an instance uniquely (i.e.~being the only solver to do so)
is showing up in the table. This is, for example the case of last listed  
cryptominisat-walksat-nolimits with otherwise relatively low number of solved instances (140).
Highlighting unique solutions is a property of the greedy set cover metric
which we believe is congruent with documenting contributions to the state of the art.

\subsection{Time-limited schedules}

The greedy set cover technique focuses only on solving the ``solvable'' instances,
disregarding the time it would take to execute the obtained schedule. We can
also look at schedules that would fit in a prescribed time budget. A natural choice
of the budget seems to be the original time limit of \SI{5000}{\second}.

\begin{table}
\caption{``Uniform time split'' schedules %using $i$ solvers 
to solve as many Main track instances as possible.}
\label{tab:MainUniformTimeSplit}
\begin{center}
\begin{tabular}{cccl}
\# solvers & time (s) & total solved & best schedule \\
\hline
1 & 5000 & 264 & Kissat-sc2020-sat \\
2 & 2500 & 278 & Kissat-sc2020-unsat, \\
             &&& Relaxed\_LCMDCBDL\_newTech \\
3 & 1666 & 272 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
			 &&& cryptominisat-ccnr-lsids \\
4 & 1250 & 262 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
			 &&& cryptominisat-ccnr-lsids, Maple-LCM-Dist-alluip-trail \\ 
5 & 1000 & 253 & Kissat-sc2020-unsat, Kissat-sc2020-sat, \\
			&&& cryptominisat-ccnr-lsids, \\
			&&& Maple-LCM-Dist-alluip-trail, cadical-alluip \\
\end{tabular}
\end{center}
\end{table}

By employing a brute-force approach we first constructed a sequences of schedules 
where the $i$-th schedule splits the available time of \SI{5000}{\second} uniformly among
$i$ solvers and solves the highest number of instances under these constraints.
The results are presented in Table~\ref{tab:MainUniformTimeSplit}.
We can see that the initial increase from 264 to 278 of ``covered'' instances 
when using two solvers instead of one (although allowing each to only use half of the time)
does not continue further with additional solvers allowed,
although its still better to use three solvers in a fair time split 
(and cover 272 instances) than just one.
One could use this observation to conjecture that the really hard 
problems that were solved actually require quite a large time to 
get ``cracked'' by any solver and thus the advantage of adding more solvers to the schedule
quickly diminishes.

We complemented ...

\newpage
